---
title: "When will it work"
output:
  html_document:
    df_print: paged
---
 
 This is based on the current Situation in Germany with approx. 30k cases 
 per day and a lockdown from 2020-12-16 onward. Effect estimates are based 
 roughly on Brauner et al. Science 2020 [link](https://science.sciencemag.org/content/early/2020/12/15/science.abd9338/).
 Roughly, because they didn't provide tables.
 
### Effects
 
 - Limit gatherings to max. 10 persons: -45%
 - Limit only some businesses: -15%
 - Limit businesses to essential activities: -25%
 - Close schools and universities: -40%
 - Additional stay-at-home orders: -15% 

### Calculations 
 
```{r}
library("tidyverse")
b117 <- .5
R0 <- 3.3
Lockdown_light_Effect = R0*(1-.45)*(1-.15)
Lockdown_light_Effect_b117 = (R0+b117)*(1-.45)*(1-.15)
Hard_Lockdown_Effect = R0*(1-.45)*(1-.25)*(1-.40)*(1-.15)
Hard_Lockdown_Effect_b117 = (R0+b117)*(1-.45)*(1-.25)*(1-.40)*(1-.15)

all_scens= data.frame('scenario'=c("light","light b 1.1.7","hard","hard b 1.1.7"),effect=c(Lockdown_light_Effect,Lockdown_light_Effect_b117,Hard_Lockdown_Effect,Hard_Lockdown_Effect_b117))

```
 
Overall estimated R(t) based on **lockdown light* should have been `r Lockdown_light_Effect`. Everything below this can be considered a success.
 
### Goal and Time to reach

Overall estimated R(t) based on **lockdown* from 2020-12-15 should be `r Hard_Lockdown_Effect`. We will use this estimate to calculate the time until the 
official threshold of 50 cases per 100k inhabitants within 7 days is reached.

```{r}
current_cases_daily = 269500/10
population = 82.5 * 1e6
goal_daily = round((population/100000)*(50)/7)
```


```{r}
estimate_duration <- function(df,goal){
  goal_daily = round((population/100000)*(goal)/7)
  newdf = df %>%
    mutate(Reduction_daily = 1*effect^.1,
           days_till_goal = round((-1*log(current_cases_daily/goal_daily)/log(Reduction_daily))),
    date = lubridate::now()-lubridate::days(1)+lubridate::days(days_till_goal),
    result = ifelse(effect<1,format(date),"never"))
  newdf$result
}
```


### So, how long for Germany 50?

The goal is to reduce the daily cases to 50 or better 20 (in light of b.1.1.7) per 7 days. This is, how long it will take:

```{r}
all_scens %>% mutate("goal 50"=estimate_duration(.,50),"gaol 20"=estimate_duration(.,7))
```






 

